Semantic authoring in a flexiformal context --- Bulk annotation of rigorous documents

### 2025-05-22 doc/cicm25-paper/paper.tex
some more fixes

\subsection{Running Example: Annotating ``terminal''}
With \sTeX, authors can add semantic references to technical terms,
which enables straight-forward learning support services like
showing the definition of a term, but also informs the system
about the content/prerequisites of a learning object.
Adding these references is a key practical problem when converting presentational {\LaTeX}
course materials into semantic documents.

@@

\begin{figure}[ht]
  \setlength{\fboxsep}{0pt}
  \fbox{\includegraphics[width=12cm,trim={0 3cm 0 0},clip]{../img/snify}}
  \caption{\snify in Action: Annotating the word ``terminal''.}\label{fig:snify}
\end{figure}

@@

In local/private archives, the \snify harvester needs to work directly on the \sTeX
sources.
Currently, \snify uses a custom Python implementation for harvesting the verbalization cache,
but we are working on a implementation based on the new \flams \textbf{linter} -- a simple \sTeX parser that
drives the LSP functionality \sTeX IDE plugins for \textsf{VSCode} and \textsf{emacs}.
% Here we have extended the \flams \textbf{linter} -- a simple \sTeX parser that
% drives the LSP functionality the VSCode and \texttt{emacs} \sTeX IDE plugins use to deal
% with definienda. This is much more efficient (and robust) than the initial regex-based
% python parser).
The analogon for this on the \WOIDE side is still under development it
could be based on \FTML generated by \WOIDE, or \WOIDE could directly export symbol/verbalization
pairs into the \snify verbalization cache.

@@

In all cases, the setting, solution, and resulting workflows differ from the one presented
in this paper. The WissKI system \cite{goerz2010adaptation} has a rudimentary text edition
facility that allows annotating document with ontology -- mostly ABox -- references; this
is the nearest match to our \snify system.

>>>>

\subsection{Running Example: Annotating ``terminal''}
With \sTeX, authors can add semantic references to technical terms,
which enables straightforward learning support services like
showing the definition of a term, but also informs the system
about the content/prerequisites of a learning object.
Adding these references is a key practical problem when converting presentational {\LaTeX}
course materials into semantic documents.

@@

\begin{figure}[ht]
  \setlength{\fboxsep}{0pt}
  \fbox{\includegraphics[width=12cm,trim={0 3cm 0 0},clip]{../img/snify}}
  \caption{\snify in Action: Annotating the word ``terminal''}\label{fig:snify}
\end{figure}

@@

In local/private archives, the \snify harvester needs to work directly on the \sTeX
sources.
Currently, \snify uses a custom Python implementation for harvesting the verbalization cache,
but we are working on a implementation based on the new \flams \textbf{linter} -- a simple \sTeX parser that
drives the LSP functionality \sTeX IDE plugins for \textsf{VSCode} and \textsf{emacs}.
% Here we have extended the \flams \textbf{linter} -- a simple \sTeX parser that
% drives the LSP functionality the VSCode and \texttt{emacs} \sTeX IDE plugins use to deal
% with definienda. This is much more efficient (and robust) than the initial regex-based
% python parser).
The analogon for this on the \WOIDE side is still under development; it
could be based on \FTML generated by \WOIDE, or \WOIDE could directly export symbol/verbalization
pairs into the \snify verbalization cache.

@@

In all cases, the setting, solution, and resulting workflows differ from the one presented
in this paper. The WissKI system \cite{goerz2010adaptation} has a rudimentary text edition
facility that allows annotating documents with ontology -- mostly ABox -- references; this
is the nearest match to our \snify system.
